---
output: github_document
bibliography: inst/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  # these options tend to vary from one Rmd to another
  echo = TRUE,
  fig.path = "man/figures/README-",
  # these options tend to remain constant
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  fig.width = 6,
  fig.asp = 1 / 1.6,
  out.width = "70%",
  fig.align = "center",
  # http://r-pkgs.had.co.nz/vignettes.html: error = TRUE captures errors in
  # the block and shows them inline. This is useful for demonstrating what
  # happens if code throws an error. If you use error = TRUE, set
  # purl = FALSE. Vignettes are accompanied by files containing all the
  # code from the vignette. purl = FALSE prevents the code from being
  # inserted into that file
  error = TRUE,
  purl = FALSE
)
knitr::knit_hooks$set(inline = function(x) {
  if (!is.numeric(x)) {
    x
  } else if (x >= 10000) {
    prettyNum(round(x, 2), big.mark = ",")
  } else {
    prettyNum(round(x, 2))
  }
})
options(tibble.print_min = 8L, tibble.print_max = 8L)
```


# graphclassmate

A package for functions and data used in data visualization courses.



## Installation

The development version can be installed from GitHub.   

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("graphdr/graphclassmate")
```


## Data

The graphclassmate package includes: 



## Usage

Stuff

## Meta

- Get citation information with `citation("graphclassmate")` 
- Please note that this project is released with a [Code of Conduct](). If you contribute to this project you agree to abide by its terms. 


